Cover Letter: Cudele (Paper 306)

### 2018-01-08 paper/cover_letter.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: typos and #40
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{document}
\title{Cover Letter: Cudele}
\maketitle

@@

For Reviewer 1, we fixed user vs. client terminology in Section~{\S}III,
clarified that the cost of dynamically changing semantics is future work in
Sections~{\S}I and~{\S}III, and added source code pointers in Section~{\S}V.
For Reviewer 2, we removed the major takeways headings and cross-references in
Section~{\S}V. For Reviewer 3, we quantified speedups with figure annotations
in Section~{\S}V. For Reviewers 1 and 3, we added servers, network, and storage
setups in Section~{\S}V. For Reviewer 4 we added descriptions to each use case
in Section~{\S}V describing how Cudele would work with Spark.

>>>>

\begin{document}
\title{Cover Letter: Cudele (Paper 306)}
\maketitle

@@

For Reviewer 1, we fixed user/client terminology in Section~{\S}III,
clarified that the cost of dynamically changing semantics is future work in
Sections~{\S}I and~{\S}III, and added source code pointers in Section~{\S}V.
For Reviewer 2, we removed the major takeaways headings and cross-references in
Section~{\S}V. For Reviewer 3, we quantified speedups with figure annotations
in Section~{\S}V. For Reviewers 1 and 3, we added servers, network, and storage
setups in Section~{\S}V. For Reviewer 4 we added descriptions to each use case
in Section~{\S}V describing how Cudele would work with Spark.

### 2018-01-08 paper/sections/6_results.tex
paper: typos and #40
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\newcomment{ ``Decoupled: merge + create" outperforms ``RPCs" by \(3.37\times\)
because ``decoupled: merge + create" uses a relaxed form of consistency and
leverages bulk updates just like DeltaFS~\cite{zheng:pdsw2015-deltafs}.
Decoupled namespaces (1)} place no restrictions on the validity of metadata
inserted into the journal ({\it e.g.}, never checking for the existence of
files before creating files), \newcomment{(2)} avoid touching poorly scaling
data structures\newcomment{, and (3) allow clients to batch events into bulk
updates}. \oldcomment{We can scale linearly if we weaken our consistency by
never checking for the existence of files before creating files ({\it i.e.}
only append \texttt{open()} requests to the journal).  When the updates are
merged by the metadata server into the in-memory metadata store they never scan
growing data structures.}  Had we implemented the \oldcomment{Append Client
Journal mechanism}\newcomment{client to send updates one at a time and} to
include \texttt{lookup()} commands before \texttt{open()} requests, we would
have seen \newcomment{performance closer to the ``RPC" subtree}\oldcomment{the
poor scaling that we see with the RPCs mechanism}. \newcomment{The ``decoupled:
merge + create" curve is also pessimistic because it models a scenario in which
all client journals arrive at the same time.} So for the 20 clients data point,
we are measuring the operations per second for 20 client journals that land on
the metadata server at the same time. \newcomment{Had we added infrastructure
to overlay journal arrivals or time client sync intervales, we could have
scaled more closely to ``decoupled: create".}\oldcomment{The ``create + merge"
bar adds the time it takes for clients to generate the journal of events in
parallel. ALSO DISCUSS 3.7X!!}

>>>>

\newcomment{ ``Decoupled: merge + create" outperforms ``RPCs" by \(3.37\times\)
because ``decoupled: merge + create" uses a relaxed form of consistency and
leverages bulk updates just like DeltaFS~\cite{zheng:pdsw2015-deltafs}.
Decoupled namespaces (1)} place no restrictions on the validity of metadata
inserted into the journal ({\it e.g.}, never checking for the existence of
files before creating files), \newcomment{(2)} avoid touching poorly scaling
data structures\newcomment{, and (3) allow clients to batch events into bulk
updates}. \oldcomment{We can scale linearly if we weaken our consistency by
never checking for the existence of files before creating files ({\it i.e.}
only append \texttt{open()} requests to the journal).  When the updates are
merged by the metadata server into the in-memory metadata store they never scan
growing data structures.}  Had we implemented the \oldcomment{Append Client
Journal mechanism}\newcomment{client to send updates one at a time and} to
include \texttt{lookup()} commands before \texttt{open()} requests, we would
have seen \newcomment{performance closer to the ``RPC" subtree}\oldcomment{the
poor scaling that we see with the RPCs mechanism}. \newcomment{The ``decoupled:
merge + create" curve is also pessimistic because it models a scenario in which
all client journals arrive at the same time.} So for the 20 clients data point,
we are measuring the operations per second for 20 client journals that land on
the metadata server at the same time. \newcomment{Had we added infrastructure
to overlay journal arrivals or time client sync intervals, we could have
scaled more closely to ``decoupled: create".}\oldcomment{The ``create + merge"
bar adds the time it takes for clients to generate the journal of events in
parallel. ALSO DISCUSS 3.7X!!}
